---
title: "blblm-pkgs"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{blblm-pkgs}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(blblm)
```

Note: This package is an application of bag of little bootstrap(BLB)
algorithm I learned from STA 141C (Big Data & High Performance
Statistical Computing)

## The bag of little bootstraps (BLB)

It is a procedure which incorporates features of both the bootstrap and
subsampling to yield a robust, computationally efficient means of
assessing the quality of estimators (i.e., construct confidence
intervals )

```{r, echo = FALSE}
DiagrammeR::grViz("blb.gv", height = 300)
```

Basically, the bag of little bootstraps = map_reduce + bootstrap.
However, for each bootstrap, we sample $n$ from $b$ with replacement
instead of sample $b$ from $b$ as in ordinary bootstrap.

-   sample without replacement the sample $s$ times into sizes of $b$

-   for each subsample

    -   resample each until sample size is $n$, $r$ times
    -   compute the bootstrap statistic (e,g., the mean of a variable,
        or cor between two variables) for each bootstrap sample
    -   compute the statistic (e.g., confidence interval) from the
        bootstrap statistics

-   take the average of the statistics

## Intro on package `blblm`

-   The main package realizes the application of BLB algorithm on Linear
    Regression Model and Logistic Regression model

-   Provide two main functions

    -   `blblm()` BLB on Linear Regression Model (Could specify
        Parallelization by setting `Parallel = TRUE`)
    -   `blbglm()` BLB on Logistic Regression Model (Could specify
        Parallelization by setting `Parallel = TRUE`)

-   Override Four functions

    -   `coef()` Obtain the coefficients for objects
    -   `confint()` Obtain the confidence intervals for coefficients
    -   `sigma()` Obtain the sigma for objects (Could specify confidence
        level by setting `confindence = TRUE`)
    -   `predict()` Predict values for new observation by given model
        (Could specify confidence level by setting `confindence = TRUE`)

### Usage of blblm

#### On `blblm`
```{r}

# Setting up the model for blblm
fitlm<-blblm(mpg ~ wt * hp, data = mtcars, m = 3, B = 100, Parallel = FALSE)

# Obtain coefficient
coef(fitlm)

# Obtain confidence Interval for coefficients
confint(fitlm, c("wt", "hp"))

# Obtain sigma 
sigma(fitlm)

# Obtain sigma with confidence intervals
sigma(fitlm, confidence = TRUE)

# Predict new observation
predict(fitlm, data.frame(wt = c(2.5, 3), hp = c(150, 170)))

# Predict new observation with confidence intervals
predict(fitlm, data.frame(wt = c(2.5, 3), hp = c(150, 170)), confidence = TRUE)

# Print
print(fitlm)
```

Turn warning = FALSE because we have a relatively small dataset
Therefore for some observation, the algorithm won't converge and will have fitted probability as 0 or 1
#### ON `blbglm`
```{r, warning=FALSE}
# Setting up the model for blblm
fitglm<-blbglm(Species ~ Sepal.Length * Sepal.Width, data = iris[1:100,], m = 3, B = 100, family = binomial, Parallel = FALSE)

# Obtain coefficient
coef(fitglm)

# Obtain confidence Interval for coefficients
confint(fitglm, c("Sepal.Length", "Sepal.Width"))

# Obtain sigma 
sigma(fitglm)

# Obtain sigma with confidence intervals
sigma(fitglm, confidence = TRUE)

# Predict new observation
predict(fitglm, data.frame(Sepal.Length = c(5.5, 5.1), Sepal.Width = c(2.3, 3.5)))

# Predict new observation with confidence intervals
predict(fitglm, data.frame(Sepal.Length = c(5.5, 5.1), Sepal.Width = c(2.3, 3.5)), confidence = TRUE)

# Print
print(fitglm)
```


#### Parallelization
```{r}
library(future)
plan(multiprocess,workers=8)
options(future.rng.onMisuse = "ignore")
```

##### blblm
```{r}
## We use system.time instead of bench::mark because the html will not give the output for bench::mark
system.time(fitlm1<-blblm(mpg ~ wt * hp, data = mtcars, m = 10, B = 5000, Parallel = FALSE))
system.time(fitlm2<-blblm(mpg ~ wt * hp, data = mtcars, m = 10, B = 5000, Parallel = TRUE))
```

##### blbglm
```{r, warning=FALSE}
system.time(fitglm1<-blbglm(Species ~ Sepal.Length * Sepal.Width, data = iris[1:100,], m = 3, B = 5000, family = binomial, Parallel = FALSE))
system.time(fitglm2<-blbglm(Species ~ Sepal.Length * Sepal.Width, data = iris[1:100,], m = 3, B = 5000, family = binomial, Parallel = TRUE))
```
As you can see, when you turn on parallization, the package will significantly improved its efficiency.
